Behavior Driven Development in Haskell

### 2012-05-22 paper.tex
adding TBD.
writing ack.

\conferenceinfo{WXYZ '05}{date, City.} 
\copyrightyear{2005} 
\copyrightdata{[to be supplied]}

\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\category{CR-number}{subcategory}{third-level}

\terms
term1, term2

@@

The text of the paper begins here.

@@

TBD: Acknowledgments, if needed.

>>>>

\conferenceinfo{Haskell Symposium 2012}{13th September, Copenhagen.}
\copyrightyear{2012}
\copyrightdata{[to be supplied]}

\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{TBD: short description of paper}   % 'preprint' option specified.

@@

\category{TBD:CR-number}{subcategory}{third-level}

\terms
TBD

@@

@@

We would like to thank
Nick Smallbone for having improved QuickCheck so that boolean property is tested
just once.
We are grateful to David Waern and Simon Marlow
for introducing the property syntax to haddock.
